Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-25 code/scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
Updated analogy section

We assume that a cognitive system will have a way of initially acquiring examples of CDSRs, e.g., by being taught through dialogue, sketching, or hand-coding. To avoid burdening potential users with the task of teaching the system every CDSR individually, it is desirable for a cognitive system to be able to automatically recognize similar regions after initial training. For example, after a janitorial robot has been taught where the front of one classroom is, it should be able to identify the fronts of other classrooms in the building. We have chosen \emph{analogy} as the approach our system will use to solve this problem, as analogy has been previously used to successfully combine semantic as well as geometric information in spatial reasoning tasks~\cite{Lockwood/etal2008}.

@@

Figure \ref{fig:analogy} illustrates a sample mapping between five base expressions and three target ones. Each oval represents a binary predicate, and its two entity arguments are represented by squares. SME generates a mapping between the base expressions \fw{(group Desk1 Desk2)} and  \fw{(xMinusYZero Desk1 Desk2)}, and the  target expressions \fw{(group Desk11 Desk12)} and \fw{(xMinusYZero Desk11 Desk12)} as well as between the \fw{regionType} expressions in each case . This is done in the following manner. First, the predicates of these expressions are placed in correspondence, as identical predicates are preferred by SME. Additional align the arguments of the aligned predicates, \fw{Desk1} with \fw{Desk11},  \fw{Desk2} with \fw{Desk12}, and \fw{CDSR1} with \fw{CDSR2}. While there is another \fw{XMinusYZero} statement in the base about two desks, it cannot correspond to either of the target expressions in the same mapping due to the one-to-one constraint in SME which allows each element in the target to map to at most one element in the base and vice versa. In Figure \ref{fig:analogy}, the correspondences are highlighted by the hashed bi-directional arrows. Next, SME creates a candidate inference for the region boundary expression, because both the mapped \fw{Group} and \fw{regionType} predicates participate in the mapping. The candidate inference is stated as \fw{(regionBoundary(:skolem CSDR1) (XMinYMost ...))}. \fw{:skolem} is used to denote entities that do not exist in the target description but are included in the candidate inferences. In this case, the candidate inference states that there is something like \fw{CSDR1} in the target, and its boundary includes the \fw{XMinYMost} point of the two desk group. Note that inference is selective, with no candidate inferences generated for the entirely unmapped expressions. %Next, we describe how we use the results of an analogy to infer a context-dependent spatial region in the target.

>>>>

We assume that a cognitive system will have a way of initially acquiring examples of CDSRs, e.g., by being taught through dialogue, sketching, or hand-coding. To avoid burdening potential users with the task of teaching the system every CDSR individually, it is desirable for a cognitive system to be able to automatically recognize similar regions after initial training. For example, after a janitorial robot has been taught where the front of one classroom is, it should be able to identify the fronts of other classrooms in the building. We have chosen \emph{analogy} as the approach our system will use to solve this problem, as analogy has been previously used to successfully combine semantic and geometric information in spatial reasoning tasks~\cite{Lockwood/etal2008}.

@@

Figure \ref{fig:analogy} illustrates a sample mapping between six base expressions and three target ones. Each oval represents a predicate, and the entity arguments are represented by squares. SME generates a mapping between the base expressions \fw{(group Desk1 Desk2)} and  \fw{(xMinusYZero Desk1 Desk2)}, and the  target expressions \fw{(group Desk11 Desk12)} and \fw{(xMinusYZero Desk11 Desk12)} as well as between the \fw{regionType} expressions in each case . This is done in the following manner. First, the predicates of these expressions are placed in correspondence, as identical predicates are preferred by SME. Then SME will align the arguments of the aligned predicates, \fw{Desk1} with \fw{Desk11},  \fw{Desk2} with \fw{Desk12}, and \fw{CDSR1} with \fw{CDSR2}. While there is another \fw{XMinusYZero} statement in the base about two desks, it cannot correspond to either of the target expressions in the same mapping due to the one-to-one constraint in SME which allows each element in the target to map to at most one element in the base and vice versa. In Figure \ref{fig:analogy}, the correspondences are highlighted by the hashed bi-directional arrows. Next, SME creates a candidate inference for the boundary segment expression, because both the mapped \fw{Group} and \fw{regionType} predicates participate in the mapping. The candidate inference is shown in red in the figure. Note that inference is selective, with no candidate inferences generated for the entirely unmapped expressions. %Next, we describe how we use the results of an analogy to infer a context-dependent spatial region in the target.
